Concurrent Programming in Harmony

### 2021-04-15 book/paper.tex
Improved barrier synch description

\autoref{fig:genbarrier} shows the code.
Method~\texttt{enter}() has two \texttt{wait} loops, one for each
waiting condition.
This is sometimes called \emph{double turnstile}.
Each loop uses a different condition variable.
The first loop waits until the car has emptied out, while
the second waits for the car to fill up.

Notice how variables \textit{entered} and \textit{left}
are maintained.  They are incremented one-by-one, but they
are not decremented one-by-one.  Instead, the last thread to
enter sets \textit{left} to zero (and notifies the threads
that were waiting to for the car to fill up), while the last
thread to exit sets \textit{entered} to zero (and notifies
the threads that were waiting for the car to empty out).

\autoref{fig:barriertest} is a test program.  The threads check
that all threads within the barrier are in the same round.

>>>>

But this poses a complication.  Suppose, for example, that there are two
seats in the car, and there is one person in the car.  Does that mean that
the car is not yet full, or not yet empty?  We have to distinguish
those situations.  To this end, it is useful to think of the car as going through
$2 \cdot n$ stages:
\begin{itemize}
\item[] Stage 0: the car is empty;
\item[] Stage $1 ... n-1$: the car is filling up;
\item[] Stage $n$: the car is full;
\item[] Stage $n+1 ... 2n - 1$: the car is emptying out.
\end{itemize}

\autoref{fig:genbarrier} shows code that implements barrier synchronization
using these stages.
Method~\texttt{enter}() has two \texttt{wait} loops, one for each
waiting condition.
This is sometimes called \emph{double turnstile}.
Each loop uses a different condition variable.
The first loop waits until the car has emptied out, while
the second waits for the car to fill up.
\autoref{fig:barriertest} is a test program.  The threads check
that all threads within the barrier are in the same round.
